Stable Neo-Hookean Flesh Simulation

### 2019-10-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on paper, forgot to git it

\textbf{1. Inversion Stability:} Given some arbitrary object it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in figure \ref{fig:inversion_1}. In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In figure \ref{fig:inversion_3} image we have an inversion of the object. The needed deformation energy has to be able to deal with both cases.

@@

\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.

>>>>

\textbf{1. Inversion Stability:} Given some arbitrary object it is possible that while deforming the object we can arrive at a zero volume state or even an entire inversion. Take for example the tetrahedron shown in figure \ref{fig:inversion_1}. In figure \ref{fig:inversion_2} we see a deformed state of this tetrahedron where the volume is scaled down to zero and we are left with a simple triangle. In figure \ref{fig:inversion_3} image we have an inversion of the object. The needed deformation energy has to be able to deal with both cases. That means that the energy has to be singularity-free and does not need any filters or threshold (\cite{Smith:2018:SNF:3191713.3180491}, 12:3).

\todoredefined[inline]{
TODO: Explain what last sentence means. Reference correct like this?
}

@@

\textbf{2. Reflection stability:} A reflection is rotation around the coordinate origin.
For the deformation energy we need it to be well behaved regardless of the reflection convention used in the singular value decomposition.
